---
title: "Reproducible Templates Final Assignment"
author: "Author: Hilary Doe"
date: "`r Sys.Date()`"
output: html_document
  #prettydoc::html_pretty:
    theme: hpstr
    highlight: github
---

```{r setup, include=FALSE}
# define knitr options
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)

# set any missing NAs in table to blank
options(knitr.kable.NA='')

# load R packages
library(fivethirtyeight)
library(tidyverse)
library(knitr)
library(kableExtra)
library(ggthemes)
```

## Information

This HTML document was created using `prettydoc` with the `hpstr` theme. I use r chunks to add the various plots and tables. As you will see, this document contains the following:

- A bullet list (see!)
- a plot of the `pressure` dataset
- the top rows of the built-in `cars` dataset.

## Plot of Pressure

The following plot has a height and width of 5.

```{r plot, fig.height=5, fig.width=5}
plot(pressure)
```

## Top 6 Rows of the Cars Dataset.

Here is a table made with the "kable_classic" theme.

```{r table} 
dt <-head(cars)

dt |>
  kbl(caption = "Top 6 Rows of Cars Dataset") |>
  kable_classic()

```
